Empirical normative theories

### 2020-07-16 simple.tex
Commands without final redundant i

\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[version=last, pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=12pt, a4paper, french, english]{scrartcl}
\input{preamble/packages}
\input{preamble/math_basics}
\input{preamble/math_mine}
\input{preamble/redac}
%\input{preamble/draw}
%\input{preamble/acronyms}
\addtokomafont{labelinglabel}{\sffamily\bfseries}
\renewcommand{\phi}{\varphi}
\DeclareMathAlphabet{\mathup}{OT1}{\familydefault}{m}{n}

@@

The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$. This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬\propposs = (¬\prop, \mathit{sure})$ and $¬\propsure = (¬\prop, \mathit{poss})$. Observe that $¬¬\phi = \phi$. (The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
As usual with binary relations, $\hist \nileadstoi \phi$ means $(\hist, \phi) \notin {\ileadsto}$.

Given $i \in I, \phi \in \Phi, \hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadsto \phi \land \hist \nileadstoi ¬\phi$.
Define $\hist \ileadstosti \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
Given $\hist \in \allhist$, let $\histend$ denote the set containing the last two elements of the sequence $\hist$ if the sequence has at least two elements; the singleton set containing the last element of the sequence if it has exactly one element; and the empty set if $\hist = \emptyset$.
Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstosti \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstosti \phi$.

\subsection{Classify propositions}
\begin{axiom}[Normative adequacy]
	\label{ax:norm}
	$\forall i \in I, \phi \in \Phi: 
		[(\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi)] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
\end{axiom}
This axiom can be simplified, thanks to the following proposition.
\begin{proposition}[Protocol coherence]
	\label{prop:protcoh}
	$\forall i \in I, \phi \in \Phi$:
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstosti ¬\phi].
	\end{equation}
\end{proposition}
\begin{proof}
	Protocol coherence is satisfied by definition of $\ileadstosti$. Indeed, if for some $\ar \in \allargs$, $\ar \ileadstosti \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadstoi ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstosti ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\phi$.
\end{proof}

Therefore, \cref{ax:norm} is actually equivalent to the following property.
\begin{property}[Simple normative adequacy]
	\label{ax:snorm}
	$\forall i \in I, \phi \in \Phi: 
		[\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
\end{property}

To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\phi \in \Phi$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi$.
The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
The next property ensures an unambiguous interpretation of the content of $\iPhi$ for all $i$-decidable propositions. In this definition, $\oplus$ denotes the exclusive disjunction; thus $\phi \in \iPhi \oplus ¬\phi \in \iPhi$ is equivalent to: $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$. It can be seen to hold by recalling that \cref{ax:snorm} is equivalent to \cref{ax:norm}.

\begin{property}[Restricted interpretability]
	\label{def:restrinterpr}
	$\forall i \in I, \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstosti \phi \lor \ar \ileadstosti ¬\phi] ⇒ [\phi \in \iPhi \oplus ¬\phi \in \iPhi]$.
\end{property}

@@

Given $\phi \in \Phi$, $\args \subseteq \allargs$ and $\ar_0 \in \allargs$, say that $\args$ seems $i$-ineffective against $\ar_0$ for $\phi$, $\args \bowtie^{i, \phi} \ar_0$, iff $\exists \hist \in \allhist \suchthat \hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0 \land \hist \ileadstosti \phi$, that is, when some $\hist$ ends with $\args$ followed by $\ar_0$ and leads to $\phi$. Note that for all $\ar_0 \in \allargs$ such that $\exists \hist \in \allhist \suchthat [\hist(l(\hist)) = \ar_0 \land \hist \ileadstosti \phi]$: $\emptyset \sinef \ar_0$.

Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeatsi \ar_0$ iff $\exists \hist \in \allhist \suchthat \ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land \ar_0 \in \histend \land \hist \nileadstoi \phi \land (\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0$.

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsiinv}](\ar)$. Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$, where $(\dip)^0$ is the identity function over $\allargs$.

$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstosti \phi$. 
%$\ar_0$ recursively $i$-defends $\phi$ iff $\forall \ar \in \cup_{k \in \N}(\dip)^k(\ar_0)$: $\ar$ $i$-defends $\phi$.

@@

A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi$.

\begin{theorem}
	An empirical theory is convincing iff it has no falsification instances.
\end{theorem}
\begin{proof}
	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstosti \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
\end{proof}

@@

	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstosti \phi$, and normative adequacy brings the conclusion.

	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstosti \phi}$. Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred$, defined as $\allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.

	Lemma: given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\allhistsznp ≠ \emptyset$, $\hist \in \allhistred ⇒ \exists \histp \in \allhistsznp \suchthat \emptyset ≠ \args^{\histp} \subset \args^{\hist}$. To see this, pick as $\histp$ any sequence consisting of the arguments contained in $\args^{\hist} \setminus \set{\ar_1}$, followed by $\ar_0$. 
	First, $\histp \in \allhistsznp$, because as $\hist \in \allhistred$, $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$, thus, $\histp \nileadstosti \phi$. 
	Second, $\args^{\histp} = \args^{\hist} \setminus \set{\ar_1}$, because $\args^{\hist} \setminus \set{\ar_1} \subseteq \args^{\histp} = \left(\gbeatsinv(\ar_0) \cap \histp\right) \subseteq \args^{\hist} \setminus \set{\ar_1}$.
	Finally, $\args^{\histp} ≠ \emptyset$ follows from two facts: that $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$ (see “First” here above) and that $\emptyset \sinef \ar_0$, which is implied by $\ar_0$ $i$-defends $\phi$.

@@

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstosti \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeatsi \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstosti \phi$. 
	By definition, $\ar_0 \nileadstosti \phi$ means that $\exists \hist \in \allhistsznp$.
	Because $\ar_0$ $i$-defends $\phi$, $\args^{\hist} ≠ \emptyset$. 
	From the preceding conclusion, we can pick some $\histp \in \allhistnonred$.
	Thus, $\exists \ar_1 \in \args^{\histp} \suchthat \args^{\histp} \setminus \set{\ar_1} \sinef \ar_0$.
	By definition, this means that $\ar_1 \ibeatsi \ar_0$ and, as $\ar_1 \in \args^{\histp} = \gbeatsinv(\ar_0) \cap \histp$, $\ar_1 \gbeats \ar_0$. 
	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1$. Defining $\ar_2 = \ar_0 + \ard_2$, by definition of $\dip$, $\ar_2 \in \dip(\ar_0)$.

	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstosti \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$. That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering $\ard_2$ and $\ar_2$ as defined in the lemma, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ard_2 \in \df(\ar_0)$ by definition of $\df$.

	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs[i, \phi]$. Given $k \in 2\N$, if $\ar_k \nileadstosti \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstosti \phi$.
\end{proof}

@@

\section{Next}
\NewDocumentCommand{\ileadstoe}{O{}}{⇝^{#1}_\exists}
\NewDocumentCommand{\nileadstoe}{O{}}{\not⇝^{#1}_\exists}
\NewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
\NewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.

@@

Discuss variant with an empirical claim: $\hist \ileadsto \phi ⇒ \hist \nileadstoi ¬\phi$; and change \cref{ax:norm}: $[\forall \hist, \hist \ileadsto \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.

@@

Let $I$ represent a given set of individuals; $\allalts$ a set of products; 
and $\allargs$ the set of all strings.
Given $i \in I$, define $\ileadstosti$ as follows. 
Given $\hist \in \allhist$ and $\phi \in \Phi_\allalts$, with $\phi \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$. Define $\hist \ileadstosti \phi$ iff $i$ chooses $a$. \commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iPhi$, thus, $\ppst$ does not have a meaningful content. Should rather define $\ppstsure$ so that $a$ is picked rather than $b$ whatever the choice set. This requires to generalize $\ileadstosti$.}

@@

A normative theory about $\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: [\exists \ar_{a \pst b} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure] \land [\exists \ar_{b \pst c} \in \allargs \suchthat \ar_{b \pst c} \ileadstosti \ppstsure[b][c]] ⇒ [\exists \ar_{a \pst c} \in \allargs \suchthat \ar_{a \pst c} \ileadstosti \ppstsure[a][c]]$.

@@

\subsubsection{Transitive arguments}
Given a normative theory and a function $\tau: \allargs × \allargs → \allargs$, say that $\tau$ is a transitive argument builder iff $\forall a ≠ b ≠ c ≠ a \in \allalts, \ar_{a \pst b}, \ar_{b \pst c} \in \allargs \suchthat \ar_{a \pst b} \ileadstosti \ppstsure \land \ar_{b \pst c} \ileadstosti \ppstsure[b][c]: \tau(\ar_{a \pst b}, \ar_{b \pst c}) \ileadstosti \ppstsure[a][c]$.

@@

\section{Decision situation}
\NewDocumentCommand{\ileadstoprop}{}{⇝^\prop}
\NewDocumentCommand{\ileadstonprop}{}{⇝^{¬\prop}}
\NewDocumentCommand \nileadsto { o }{%
	\IfValueTF{#1}{%
		\not⇝^{#1}%
	}{%
		\not⇝%
	}%
}
\NewDocumentCommand{\ileadstosts}{}{⇝_*}
\NewDocumentCommand{\ileadstos}{}{\overset{s}{⇝_i}}
\NewDocumentCommand{\ileadstostw}{O{}}{⇝^\mathit{w}_\forall}
\NewDocumentCommand{\ileadstostp}{O{}}{⇝^\mathit{pos}_\forall}
\NewDocumentCommand{\nileadstosts}{}{\not⇝_*}
\NewDocumentCommand{\Ti}{}{T_i}
\NewDocumentCommand{\ibeatse}{O{}}{⊳^{#1}_\exists}
\NewDocumentCommand \ibeatseinv { o }{
	\IfValueTF{#1}{%
		{⊳_\exists^{#1}}^{-1}%
	}{%
		⊳_\exists^{-1}%
	}%
}
\NewDocumentCommand{\zar}{}{\mathbf{0}}%zero, or empty, argument
\NewDocumentCommand{\mPhi}{}{\Phi_\gamma}
\NewDocumentCommand{\argsd}{}{S^\mathit{d}}

>>>>

\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[version=last, pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=12pt, a4paper, french, english]{scrartcl}
\input{preamble/packages}
\input{preamble/math_basics}
\input{preamble/math_mine}
\input{preamble/redac}
%\input{preamble/draw}
%\input{preamble/acronyms}
\addtokomafont{labelinglabel}{\sffamily\bfseries}
\renewcommand{\phi}{\varphi}%TODO
\DeclareMathAlphabet{\mathup}{OT1}{\familydefault}{m}{n}

@@

The symbol $¬$ is a negation operator on $\allprops$, such that $\forall \prop \in \allprops: ¬¬\prop = \prop$. This article also uses this symbol as a negation operator on $\Phi$, defined as follows, $\forall \prop \in \allprops$: $¬\propposs = (¬\prop, \mathit{sure})$ and $¬\propsure = (¬\prop, \mathit{poss})$. Observe that $¬¬\phi = \phi$. (The symbol $¬$ is also used in this article to negate classical mathematical propositions; this should create no confusion.)
As usual with binary relations, $\hist \nileadsto \phi$ means $(\hist, \phi) \notin {\ileadsto}$.

Given $i \in I, \phi \in \Phi, \hist \in \allhist$, say that $\hist$ leads strongly to $\phi$ iff $\hist \ileadsto \phi \land \hist \nileadsto ¬\phi$.
Define $\hist \ileadstost \phi$ iff $[\hist \text{ leads strongly to } \phi] \land [\phi = \propsure ⇒ \hist \text{ leads strongly to } \propposs]$.
Given $\hist \in \allhist$, let $\histend$ denote the set containing the last two elements of the sequence $\hist$ if the sequence has at least two elements; the singleton set containing the last element of the sequence if it has exactly one element; and the empty set if $\hist = \emptyset$.
Given $i \in I, \phi \in \Phi, \ar \in \allargs$, define $\ar \ileadstost \phi$ iff $\forall \hist \in \allhist \suchthat \ar \in \histend: \hist \ileadstost \phi$.

\subsection{Classify propositions}
\begin{axiom}[Normative adequacy]
	\label{ax:norm}
	$\forall i \in I, \phi \in \Phi: 
		[(\exists \ar \in \allargs \suchthat \ar \ileadstost \phi) \land ¬(\exists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi)] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
\end{axiom}
This axiom can be simplified, thanks to the following proposition.
\begin{proposition}[Protocol coherence]
	\label{prop:protcoh}
	$\forall i \in I, \phi \in \Phi$:
	\begin{equation}
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ [\nexists \ar \in \allargs \suchthat \ar \ileadstost ¬\phi].
	\end{equation}
\end{proposition}
\begin{proof}
	Protocol coherence is satisfied by definition of $\ileadstost$. Indeed, if for some $\ar \in \allargs$, $\ar \ileadstost \phi$, then $\forall \ar_1 \in \allargs: (\ar_1, \ar) \nileadsto ¬\phi$; thus, for any $\ar' \in \allargs$, $\ar' \ileadstost ¬\phi$ is false, because it requires that $\forall \ar_1 \in \allargs: (\ar', \ar_1) \ileadsto ¬\phi$, and thus in particular, that $(\ar', \ar) \ileadsto ¬\phi$.
\end{proof}

Therefore, \cref{ax:norm} is actually equivalent to the following property.
\begin{property}[Simple normative adequacy]
	\label{ax:snorm}
	$\forall i \in I, \phi \in \Phi: 
		[\exists \ar \in \allargs \suchthat \ar \ileadstost \phi] ⇒ \phi \in \iPhi \land ¬\phi \notin \iPhi.$
\end{property}

To further analyze this and related matters, given a normative theory and $i \in I$, say that a proposition $\phi \in \Phi$ is \emph{$i$-decidable} iff $\exists \ar \in \allargs \suchthat \ar \ileadstost \phi \lor \ar \ileadstost ¬\phi$.
The $i$-decidable propositions are those on which the normative theory permits to take a position. It will generally be unknown in practical applications, and may be empty.
The next property ensures an unambiguous interpretation of the content of $\iPhi$ for all $i$-decidable propositions. In this definition, $\oplus$ denotes the exclusive disjunction; thus $\phi \in \iPhi \oplus ¬\phi \in \iPhi$ is equivalent to: $\phi \in \iPhi ⇔ ¬\phi \notin \iPhi$. It can be seen to hold by recalling that \cref{ax:snorm} is equivalent to \cref{ax:norm}.

\begin{property}[Restricted interpretability]
	\label{def:restrinterpr}
	$\forall i \in I, \phi \in \Phi: [\exists \ar \in \allargs \suchthat \ar \ileadstost \phi \lor \ar \ileadstost ¬\phi] ⇒ [\phi \in \iPhi \oplus ¬\phi \in \iPhi]$.
\end{property}

@@

Given $\phi \in \Phi$, $\args \subseteq \allargs$ and $\ar_0 \in \allargs$, say that $\args$ seems $i$-ineffective against $\ar_0$ for $\phi$, $\args \bowtie^{i, \phi} \ar_0$, iff $\exists \hist \in \allhist \suchthat \hist(\intvl{l(\hist)-\card{\args}, l(\hist)-1}) = \args \land \hist(l(\hist)) = \ar_0 \land \hist \ileadstost \phi$, that is, when some $\hist$ ends with $\args$ followed by $\ar_0$ and leads to $\phi$. Note that for all $\ar_0 \in \allargs$ such that $\exists \hist \in \allhist \suchthat [\hist(l(\hist)) = \ar_0 \land \hist \ileadstost \phi]$: $\emptyset \sinef \ar_0$.

Given $i \in I, \phi \in \Phi, \ar_1, \ar_0 \in \allargs$, define $\ar_1 \ibeats \ar_0$ iff $\exists \hist \in \allhist \suchthat \ar_1 \in (\gbeatsinv(\ar_0) \cap \hist) \land \ar_0 \in \histend \land \hist \nileadsto \phi \land (\gbeatsinv(\ar_0) \cap \hist) \setminus \set{\ar_1} \sinef \ar_0$.

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the \emph{$\phi$-defensors of $\ar$ required for $i$}, $\di(\ar) \subseteq \alldargs$, as $\di(\ar) = [\dbeatsinv \circ {\ibeatsinv}](\ar)$. Define $\dip: \allargs → \allargs$ as $\dip(\ar) = \ar + \di(\ar)$.
Given $i \in I, \phi \in \gPhi$, define $\gargs[i, \phi] \subseteq \allargs$ as the transitive closure of ${\gleadstoinv}(\phi)$ under $\dip$: $\gargs[i, \phi] = \cup_{k \in \N} (\dip)^k({\gleadstoinv}(\phi))$, where $(\dip)^0$ is the identity function over $\allargs$.

$\ar$ $i$-defends $\phi$ iff $\forall \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset\right]: \hist \ileadstost \phi$. 
%$\ar_0$ recursively $i$-defends $\phi$ iff $\forall \ar \in \cup_{k \in \N}(\dip)^k(\ar_0)$: $\ar$ $i$-defends $\phi$.

@@

A \emph{falsification instance} of an empirical theory is a tuple $(i, \phi, \hist) \in I × \gPhi × \allhist$ such that $\exists \ar \in (\histend \cap \gargs[i, \phi]) \suchthat \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi$.

\begin{theorem}
	An empirical theory is convincing iff it has no falsification instances.
\end{theorem}
\begin{proof}
	For all $i \in I, \phi \in \gPhi$: $\exists \ar \in \gargs[i, \phi]$ that does not $i$-defend $\phi$ iff $\exists \ar \in \gargs[i, \phi], \hist \in \allhist \suchthat \left[\ar \in \histend \land \gbeatsinv(\ar) \cap \hist = \emptyset \land \hist \nileadstost \phi\right]$ iff $\exists \hist \in \allhist$ such that $(i, \phi, \hist)$ is a falsification instance.
\end{proof}

@@

	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$, and normative adequacy brings the conclusion.

	Given any $\ar_0 \in \allargs$, define $\args^{\hist} = \gbeatsinv(\ar_0) \cap \hist$ and $\allhistsznp = \set{\hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi}$. Given $\hist \in \allhistsznp$, say that $\hist$ is \emph{reducible} iff $\hist \in \allhistred$, defined as $\allhistred = \set{\hist \in \allhistsznp \suchthat \forall \ar_1 \in \args^{\hist}: \args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0}$; define accordingly $\allhistnonred = \allhistsznp \setminus \allhistred = \set{\hist \in \allhistsznp \suchthat \exists \ar_1 \in \args^{\hist} \suchthat \args^{\hist} \setminus \set{\ar_1} \sinef \ar_0}$.

	Lemma: given any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$, if $\allhistsznp ≠ \emptyset$, $\hist \in \allhistred ⇒ \exists \histp \in \allhistsznp \suchthat \emptyset ≠ \args^{\histp} \subset \args^{\hist}$. To see this, pick as $\histp$ any sequence consisting of the arguments contained in $\args^{\hist} \setminus \set{\ar_1}$, followed by $\ar_0$. 
	First, $\histp \in \allhistsznp$, because as $\hist \in \allhistred$, $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$, thus, $\histp \nileadstost \phi$. 
	Second, $\args^{\histp} = \args^{\hist} \setminus \set{\ar_1}$, because $\args^{\hist} \setminus \set{\ar_1} \subseteq \args^{\histp} = \left(\gbeatsinv(\ar_0) \cap \histp\right) \subseteq \args^{\hist} \setminus \set{\ar_1}$.
	Finally, $\args^{\histp} ≠ \emptyset$ follows from two facts: that $\args^{\hist} \setminus \set{\ar_1} \not\sinef \ar_0$ (see “First” here above) and that $\emptyset \sinef \ar_0$, which is implied by $\ar_0$ $i$-defends $\phi$.

@@

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \ar_1 \in \allargs, \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1 \ibeats \ar_0 \land \ar_1 \gbeats \ar_0 \land \ar_2 = \ar_0 + \ard_2 \in \dip(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhistsznp$.
	Because $\ar_0$ $i$-defends $\phi$, $\args^{\hist} ≠ \emptyset$. 
	From the preceding conclusion, we can pick some $\histp \in \allhistnonred$.
	Thus, $\exists \ar_1 \in \args^{\histp} \suchthat \args^{\histp} \setminus \set{\ar_1} \sinef \ar_0$.
	By definition, this means that $\ar_1 \ibeats \ar_0$ and, as $\ar_1 \in \args^{\histp} = \gbeatsinv(\ar_0) \cap \histp$, $\ar_1 \gbeats \ar_0$. 
	It now follows from the definition of an empirical theory that $\dbeatsinv(\ar_1)$ is not empty, thus, $\exists \ard_2 \in \allargs \suchthat \ard_2 \dbeats \ar_1$. Defining $\ar_2 = \ar_0 + \ard_2$, by definition of $\dip$, $\ar_2 \in \dip(\ar_0)$.

	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs[i, \phi] \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs[i, \phi] \cap \dfp(\ar_0)$. That is because $\ar_0 \in \gargs[i, \phi] ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering $\ard_2$ and $\ar_2$ as defined in the lemma, $\ar_2 \in \gargs[i, \phi]$ by definition of $\gargs[i, \phi]$ and $\ard_2 \in \df(\ar_0)$ by definition of $\df$.

	To prove the theorem, build a finite sequence of arguments in $\gargs[i, \phi]$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs[i, \phi]$. Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the last lemma, obtaining $\ar_{k + 2} \in \gargs[i, \phi] \cap \dfp^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat \dfp^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
\end{proof}

@@

\section{Next}
\NewDocumentCommand{\ileadstoe}{O{}}{⇝^{#1}_\exists}
\NewDocumentCommand{\nileadstoe}{O{}}{\not⇝^{#1}_\exists}
Define a way of saying “we never need this argument”: either the model can prove phi without s0, or if it can’t, then phi does not hold, because I can play s1 against it.

@@

Discuss variant with an empirical claim: $\hist \ileadsto \phi ⇒ \hist \nileadsto ¬\phi$; and change \cref{ax:norm}: $[\forall \hist, \hist \ileadsto \propposs] ⇒ \propposs \in \iPhi$, … This is essentially what will be done in the following, I suppose.

@@

Let $I$ represent a given set of individuals; $\allalts$ a set of products; 
and $\allargs$ the set of all strings.
Given $i \in I$, define $\ileadstost$ as follows. 
Given $\hist \in \allhist$ and $\phi \in \Phi_\allalts$, with $\phi \in \set{\ppst} × \set{\mathit{sure}, \mathit{poss}}$ for some $a ≠ b \in \allalts$, the individual is presented the arguments in $\hist$, and has then to choose a product from the set $\set{a, b}$. Define $\hist \ileadstost \phi$ iff $i$ chooses $a$. \commentOC{This is inadequate: if $i$ picks $b$ from $\set{a, b, c}$, the current definition considers it compatible with $\ppstsure \in \iPhi$, thus, $\ppst$ does not have a meaningful content. Should rather define $\ppstsure$ so that $a$ is picked rather than $b$ whatever the choice set. This requires to generalize $\ileadstost$.}

@@

A normative theory about $\allalts$ is transitive iff $\forall a ≠ b ≠ c ≠ a \in \allalts: [\exists \ar_{a \pst b} \in \allargs \suchthat \ar_{a \pst b} \ileadstost \ppstsure] \land [\exists \ar_{b \pst c} \in \allargs \suchthat \ar_{b \pst c} \ileadstost \ppstsure[b][c]] ⇒ [\exists \ar_{a \pst c} \in \allargs \suchthat \ar_{a \pst c} \ileadstost \ppstsure[a][c]]$.

@@

\subsubsection{Transitive arguments}
Given a normative theory and a function $\tau: \allargs × \allargs → \allargs$, say that $\tau$ is a transitive argument builder iff $\forall a ≠ b ≠ c ≠ a \in \allalts, \ar_{a \pst b}, \ar_{b \pst c} \in \allargs \suchthat \ar_{a \pst b} \ileadstost \ppstsure \land \ar_{b \pst c} \ileadstost \ppstsure[b][c]: \tau(\ar_{a \pst b}, \ar_{b \pst c}) \ileadstost \ppstsure[a][c]$.

@@

\section{Decision situation}
\NewDocumentCommand{\ileadstoprop}{}{⇝^\prop}
\NewDocumentCommand{\ileadstonprop}{}{⇝^{¬\prop}}
\NewDocumentCommand{\ileadstosts}{}{⇝_*}
\NewDocumentCommand{\ileadstos}{}{\overset{s}{⇝_i}}
\NewDocumentCommand{\ileadstostw}{O{}}{⇝^\mathit{w}_\forall}
\NewDocumentCommand{\ileadstostp}{O{}}{⇝^\mathit{pos}_\forall}
\NewDocumentCommand{\nileadstosts}{}{\not⇝_*}
\NewDocumentCommand{\Ti}{}{T_i}
\NewDocumentCommand{\ibeatse}{O{}}{⊳^{#1}_\exists}
\NewDocumentCommand \ibeatseinv { o }{
	\IfValueTF{#1}{%
		{⊳_\exists^{#1}}^{-1}%
	}{%
		⊳_\exists^{-1}%
	}%
}
\NewDocumentCommand{\zar}{}{\mathbf{0}}%zero, or empty, argument
\NewDocumentCommand{\mPhi}{}{\Phi_\gamma}
\NewDocumentCommand{\argsd}{}{S^\mathit{d}}
\RenewDocumentCommand{\ileadstost}{O{}}{⇝^{#1}_\forall}
\RenewDocumentCommand{\nileadstost}{O{}}{\not⇝^{#1}_\forall}
